Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Added CAROUGE values for human judges
Changed table captions
fixed grammar

In this work we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN). We apply different models to our dataset of scientifix papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.

@@

\paragraph{Abstractive text summarization} allows us to write summaries that are almost as good as those written by humans. Generally speaking, abstractive models perform worse than extractive ones. They are hard to train and often deviate too much from the original text. And since they try to describe the meaning of a text using different words, they preserve less information. Nevertheless, abstractive summarization is closer to what humans do when they write text summaries, and for that reason this is a very promissing AI topics.

@@

In this study we focus on abstractive text summarization. We do a brief overview of the related work that has been done in this field. Then we proceed to discussing different models for statistical and deep summarization. Then we present our dataset of scientific papers collected from arXiv and compare the performance of different models on this dataset.

@@

This September Li et al. \cite{li-cohn-17} described their submission to the sentiment analysis sub-task of ?Build It, Break It: The Language Edition (BIBI)? where they successfully apply generative approach to the problem of sentiment analysis.

@@

In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.

@@

\paragraph{Structure of the data} Each paper on arXiv has a unique identifier (for eample: 1801.01587). It can be used to extract any data that is available and related to that paper, including its metadata and full text as PDF.

@@

Our script\footnote{Code and instructions for collecting the data is available in our repository: \url{https://github.com/Carouge/TextSummarization}} can be used to collect more data, but for our problem a set of 2000 papers from one category is enough. For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.

\paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text. This produced a huge amount of uniterpretable UTF-8 characters from mathematical expressions. After removing those extra characters.

We wanted to remove everething that is not a known English word, but that would filter out words like "GAN", "backprop" etc. as most standard corpuses of words, such as nltk.corpus, don't include specialized scientific terminology. So we filtered the words using manually created rules based on features like word length and frequence of vowels. This leaves some noise behind, but it will not affect our models.

@@

Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.

@@

We can build a graph of each document where words or sentences are nodes and the edges are the connections between each pair of nodes. The weights on these edges represent similarity between words or sentences in the whole text. While proving to have better results than simple frequency-based methods, graph models are still bounded by the absence of lexic understanding and ability to perform extractive summary only.

@@

Evaluating a summary is a difficult task because there is no such thing as a single summary that would be ideal for a given document. In most cases even human evaluators can not agree on which of the given summaries is better\cite{das-7}. Unlike other NLP problems, such as translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad. Therefore we must make assumptions about the space of good summaries.

\begin{enumerate}
\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
\end{enumerate}

In the following sections we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).

@@

The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}.

@@

ROUGE works well for extractive text summarization. But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.

@@

We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of good summaries. Our assumption is that a good summary of a document contains words that are semantically close to the most important words or n-grams in that document.

@@

The metric we propose is in fact a continuous version of ROUGE-N. Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text. Its main advantages include  time efﬁciency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score. Unlike RAKE which operates n-grams, TextRank generates summaries using whole sentences. For that reason the generated summaries are more readable.

@@

\begin{center}
\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
\hline
\textbf{Title} & Churn Prediction in Mobile Social Games: Towards a Complete Assessment Using Survival Ensembles \\
\hline
\textbf{Real abstract} & ...for each player, we predict the probability of churning as function of time, which permits to distinguish various levels of loyalty profiles ... Our results show that churn prediction by survival ensembles significantly improves the accuracy and robustness of traditional analyses, like Cox regression... \\
\hline
\textbf{\makecell[l]{Generated \\ abstract}} & Conditional inference survival ensembles are constructed based on unbiased trees avoiding this problem the resulting prediction of this model contains for each player a survival function indicating the probability of churn as a function of time since the registration in the game. \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

After some training our model was able to generate meaningful titles for most abstracts. Take a look at this example:

@@

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
Human & 0.77 & 0.43 & 0 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In this paper we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.

@@

% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.

>>>>

In this work, we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN). We apply different models to our dataset of scientific papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.

@@

\paragraph{Abstractive text summarization} allows us to write summaries that are almost as good as those written by humans. Generally speaking, abstractive models perform worse than extractive ones. They are hard to train and often deviate too much from the original text. And since they try to describe the meaning of a text using different words, they preserve less information. Nevertheless, abstractive summarization is closer to what humans do when they write text summaries, and for that reason, this is a very promising AI topics.

@@

In this study, we focus on abstractive text summarization. We do a brief overview of the related work that has been done in this field. Then we proceed to discuss different models for statistical and deep summarization. Then we present our dataset of scientific papers collected from arXiv and compare the performance of different models on this dataset.

@@

This September Li et al. \cite{li-cohn-17} described their submission to the sentiment analysis sub-task of Build It, Break It: The Language Edition (BIBI) where they successfully apply a generative approach to the problem of sentiment analysis.

@@

In contrast, Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.

@@

\paragraph{Structure of the data} Each paper on arXiv has a unique identifier (for example: 1801.01587). It can be used to extract any data that is available and related to that paper, including its metadata and full text as PDF.

@@

Our script\footnote{Code and instructions for collecting the data are available in our repository: \url{https://github.com/Carouge/TextSummarization}} can be used to collect more data, but for our problem, a set of 2000 papers from one category is enough. For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the field of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.

\paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text. This produced a huge amount of uninterpretable UTF-8 characters from mathematical expressions. After removing those extra characters.

We wanted to remove everything that is not a known English word, but that would filter out words like "GAN", "backprop" etc. as most standard corpora of words, such as nltk.corpus, don't include specialized scientific terminology. So we filtered the words using manually created rules based on features like word length and frequency of vowels. This leaves some noise behind, but it will not affect our models.

@@

Three main classes of models that are used for a text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.

@@

We can build a graph of each document where words or sentences are nodes and the edges are the connections between each pair of nodes. The weights on these edges represent similarity between words or sentences in the whole text. While proving to have better results than simple frequency-based methods, graph models are still bounded by the absence of lexical understanding and ability to perform extractive summary only.

@@

Evaluating a summary is a difficult task because there is no such thing as a single summary that would be ideal for a given document. In most cases, even human evaluators cannot agree on which of the given summaries is better\cite{das-7}. Unlike other NLP problems, such as translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad. Therefore we must make assumptions about the space of good summaries.

\begin{enumerate}
\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
\item assume that the goodness of summary can be measured as the amount of important information it contains (this assumption can be inferred from the definition of text summarization).
\end{enumerate}

In the following sections, we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).

@@

The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) introduced by Chin-Yew Lin in 2004\cite{lin-4}.

@@

ROUGE works well for extractive text summarization. But if we need to evaluate the generated summary which contains different words from the ones that occurred in the paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.

@@

We propose a metric that uses word embeddings to evaluate summaries based on their semantic distance to the space of good summaries. Our assumption is that a good summary of a document contains words that are semantically close to the most important words or n-grams in that document.

@@

The metric we propose is, in fact, a continuous version of ROUGE-N. Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semantic distance between those n-grams.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurrence with other words in the text. Its main advantages include time efﬁciency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

\subsection{TextRank}
In this research, we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score. Unlike RAKE which operates n-grams, TextRank generates summaries using whole sentences. For that reason, the generated summaries are more readable.

@@

\begin{center}
\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
\hline
\textbf{Title} & Churn Prediction in Mobile Social Games: Towards a Complete Assessment Using Survival Ensembles \\
\hline
\textbf{Real abstract} & ...for each player, we predict the probability of churning as the function of time, which permits to distinguish various levels of loyalty profiles ... Our results show that churn prediction by survival ensembles significantly improves the accuracy and robustness of traditional analyses, like Cox regression... \\
\hline
\textbf{\makecell[l]{Generated \\ abstract}} & Conditional inference survival ensembles are constructed based on unbiased trees avoiding this problem the resulting prediction of this model contains for each player a survival function indicating the probability of churn as a function of time since the registration in the game. \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

After some training, our model was able to generate meaningful titles for most abstracts. Take a look at this example:

@@

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
Human & 0.77 & 0.43 & 0.98 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In this paper, we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.

@@

% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their pieces of advice.
